Deciding to Disclose

### 2015-09-26 Results.tex
Tweaks
Tweaking figure placement

@@

@@

\begin{figure}[H]
\includegraphics[width=100mm]{figures/sharing_emulated_simulated}
\caption{Median moderate drinker signal vs median between drinking type IQR for all decision rules, with signals coded as 0 = light, 1 = moderate, and 2 = heavy.}
\label{fig:outcome_plots}
\end{figure}

>>>>

\begin{figure}[H]
\includegraphics[width=100mm]{figures/honesty_plot}
\caption{Average fraction of population ever signalled honestly by each appointment, after 1000 rounds, mean with 95\% confidence limit over 1000 runs. Note that the large number of runs leads to very tight confidence intervals.\label{fig:honest_signals}}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=90mm]{figures/sharing_emulated_simulated}
\caption{Median moderate drinker signal vs median between drinking type IQR for all decision rules, with signals coded as 0 = light, 1 = moderate, and 2 = heavy.}
\label{fig:outcome_plots}
\end{figure}

@@
